---
title: "Stock Analysis with Quantmod"
Name: Rajiv Basnet
---

## Analysis of Stock Trends and Visualizations

The tools used are R packages quantmod and Quandl.

List of Stocks:

Google (GOOG),
Amazon (AMZN),
Bank of America (BAC),
Gold (GLD)

List of Functions and Common Indicators:

addSMA() - Simple Moving Average,
addMACD() - Moving Average Convergence Divergence,
addBBands() - Bollinger Bands,
addCCI() - Commodity channel index,
addADX() - Directional Movement Indicator,
addCMF()  - Add Chaiken Money Flow

For others, see https://en.wikipedia.org/wiki/Technical_analysis

```{r, results = 'hide'}
## install.packages("quantmod")
library(quantmod)
```

The getSymbols function loads (downloads) historic price data Usage.

## ^GSPC - S&P 500 

Retrieving data for GSPC and putting in an environment named "data".

Printing last ten lines of dataset from data environment.


```{r, echo = FALSE, results = 'hide'}

getSymbols("AMZN", src = "yahoo", from =  as.Date("2019-01-01"), to = as.Date("2019-05-01"))
tail(AMZN,10)
getSymbols("GOOG", src = "yahoo", from =  as.Date("2019-01-01"), to = as.Date("2019-05-01"))
tail(GOOG,10)
getSymbols("BAC", src = "yahoo", from =  as.Date("2019-01-01"), to = as.Date("2019-05-01"))
tail(BAC,10)
getSymbols("GLD", src = "yahoo", from =  as.Date("2019-01-01"), to = as.Date("2019-05-01"))
tail(GLD,10)
getSymbols("^GSPC", src = "yahoo", from =  as.Date("2019-01-01"), to = as.Date("2019-05-01"))
tail(GSPC,10)

```

Chart series prints candle chart with volume at bottom, for all records in 2018.

```{r}
chartSeries(AMZN,subset="2019",theme="white")
chartSeries(GOOG,subset="2019",theme="white")
chartSeries(BAC,subset="2019",theme="white")
chartSeries(GLD,subset="2019",theme="white")
chartSeries(GSPC,subset="2019",theme="white")
```


Design (theme) changes to make more visible 
```{r}
whiteTheme <- chartTheme("white") 

## List of desig options in "theme" function
names(whiteTheme)

whiteTheme$bg.col <- "white"
whiteTheme$dn.col <- "pink"
whiteTheme$up.col <- "lightgreen"
whiteTheme$border <- "lightgray"
x1 <- chartSeries(AMZN,subset="last 3 months",theme=whiteTheme,TA=NULL) 
x2 <- chartSeries(GOOG,subset="last 3 months",theme=whiteTheme,TA=NULL) 
x3 <- chartSeries(BAC,subset="last 3 months",theme=whiteTheme,TA=NULL) 
x4 <- chartSeries(GLD,subset="last 3 months",theme=whiteTheme,TA=NULL) 
x5 <- chartSeries(GSPC,subset="last 3 months",theme=whiteTheme,TA=NULL) 
class(x1)
class(x2)
class(x3)
class(x4)
class(x5)
```


Provide title for chart:
```{r}
chartSeries(AMZN["2019"],theme=whiteTheme,name="Amazon")
chartSeries(GOOG["2019"],theme=whiteTheme,name="Google")
chartSeries(BAC["2019"],theme=whiteTheme,name="Bank of America")
chartSeries(GLD["2019"],theme=whiteTheme,name="Gold")
chartSeries(GSPC["2019"],theme=whiteTheme,name="S&P 500")
```


Two years - 2018 & whatever available for 2019
```{r}
chartSeries(AMZN["2018/2019"],theme=whiteTheme,name="Amazon")
chartSeries(GOOG["2018/2019"],theme=whiteTheme,name="Google")
chartSeries(BAC["2018/2019"],theme=whiteTheme,name="Bank of America")
chartSeries(GLD["2018/2019"],theme=whiteTheme,name="Gold")
chartSeries(GSPC["2018/2019"],theme=whiteTheme,name="S&P 500")
```

Comparing the median return ratios:

```{r}

returnAMZN<-annualReturn(AMZN, subset="2018/2019") 
median(returnAMZN)
returnGOOG<-annualReturn(GOOG, subset="2018/2019") 
median(returnGOOG)
returnBAC<-annualReturn(BAC, subset="2018/2019") 
median(returnBAC)
returnGLD<-annualReturn(GLD, subset="2018/2019") 
median(returnGLD)
returnGSPC<-annualReturn(GSPC, subset ="2018/2019") 
median(returnGSPC)
```


SPY is a S&P 500 ETF (exchange traded fund).
An ETF is traded on a major stock exchange—like the New York Stock Exchange or Nasdaq.
It is a basket of stocks, in this case all the individual stocks on the S&P 500 


```{r}
getSymbols("SPY", from="2019-01-01")
class(SPY)
head(SPY)
```

Chart Item together for comparison

```{r}
chart_Series(Cl(GSPC), subset = "2019")
add_TA(Cl(AMZN), on = 1, col = "black")
add_TA(Cl(GOOG), on = 1, col = "red")
add_TA(Cl(BAC), on = NA, col = "green")
add_TA(Cl(GLD), on = NA, col = "blue")
```


Combine additional securities with normalization

To see relative changes more easily, you can normalise your price series in many ways. This is a typical approach (using a 0 origin is what Google charts does):

```{r}
normalise_series <- function(xdat) xdat / coredata(xdat)[1]
window <- "2019/"

# Define colour of default chart line to chart_Series in mytheme object
# which is passed to chart_Series:
mytheme <- chart_theme()
mytheme$col$line.col <- "gold"
chart_Series(normalise_series(Cl(GSPC)[window]) - 1, theme = mytheme)
add_TA(normalise_series(Cl(AMZN)[window]) - 1, on = 1, col = "black", lty = 3)
add_TA(normalise_series(Cl(GOOG)[window]) - 1, on = 1, col = "red", lty = 3)
add_TA(normalise_series(Cl(BAC)[window]) - 1, on = 1, col = "green", lty = 3)
add_TA(normalise_series(Cl(GLD)[window]) - 1, on = 1, col = "blue", lty = 3)

# Or add RSIs on different subpanels to improve readability of charts:
#add_TA(RSI(Cl(AMZN)), on = NA, col = "black")
#add_TA(RSI(Cl(GOOG)), on = 2, col = "red", lty = 3)
#add_TA(RSI(Cl(BAC)), on = NA, col = "green", lty = 2)
#add_TA(RSI(Cl(GLD)), on = NA, col = "blue", lty = 2)
#add_TA(RSI(Cl(GSPC)), on = NA, col = "orange", lty = 2)


```

Get Stock Dividends

```{r}
(div <- getDividends("GOOG"))
```


Get Returns (Profit or Loss from beginning of period)

```{r}

# Quick returns - quantmod style
 
## getSymbols("SBUX")
dreturns<-dailyReturn(GOOG) # returns by day
head(dreturns)

wreturns<-weeklyReturn(GOOG) # returns by week
summary(wreturns)

mreturns<-monthlyReturn(GOOG) # returns by month, indexed by yearmon
mreturns
 

```


All Returns summary compared

```{r}

# daily,weekly,monthly,quarterly, and yearly
allreturns<-allReturns(GSPC) # note the plural
summary(allreturns)
```



Get Price Earnings ratio:

```{r}
getQuote("AMZN", what = yahooQF("P/E Ratio"))
getQuote("GOOG", what = yahooQF("P/E Ratio"))
getQuote("BAC", what = yahooQF("P/E Ratio"))
getQuote("GLD", what = yahooQF("P/E Ratio"))
getQuote("^GSPC", what = yahooQF("P/E Ratio"))

```

Get Price Earnings Ratio:

```{r}
require(quantmod)
require("plyr")
what_metrics <- yahooQF(c("Price/Sales", 
                          "P/E Ratio",
                          "Price/EPS Estimate Next Year",
                          "PEG Ratio",
                          "Dividend Yield", 
                          "Market Capitalization"))

tickers <- c("AAPL", "GOOG", "AMZN", "BAC", "GS")
# Not all the metrics are returned by Yahoo.
metrics <- getQuote(paste(tickers, sep="", collapse=";"), what=what_metrics)

#Add tickers as the first column and remove the first column which had date stamps
metrics <- data.frame(Symbol=tickers, metrics[,2:length(metrics)]) 

#Change colnames
colnames(metrics) <- c("Symbol", "P/E Ratio", "P/E EPS next year", "Div Yield", "Market Cap")

head(metrics,10)
#Persist this to the csv file
## write.csv(metrics, "FinancialMetrics.csv", row.names=FALSE)
```

Use Quandl to get gross domestic product
```{r}

# install.packages("Quandl")
library(Quandl)
# Import GDP data from FRED
Quandl.api_key("szb8F2ei__rwj7mD3ugt")
gdp <- Quandl(code = "FRED/GDP")

# Look at the structure of the object returned by Quandl

str(gdp)

head(gdp,20)
```


Download interest rate (DTB3) and GDP (Gross Domestic Product) data from FRED
DTB3 = 3 month treasury bill

```{r}
getSymbols('DTB3',src='FRED')
first(DTB3,'1 week')

getSymbols('GDP',src='FRED') ## quarterly
first(GDP,'1 week')
tail(GDP)
```

```{r}
chartSeries(DTB3,theme="white",minor.ticks=FALSE)
```


Get data for currency (GBP = British Pound)
```{r}
data <- new.env()
getSymbols("GBP", from="2019-01-01", to="2019-05-01", env = data, auto.assign = T)
head(data$GBP)
plot(data$GBP)
barChart(data$GBP,TA='addSMA(n = 7, col = "red")
addSMA(n = 44, col = "blue")', subset='2019-01-01/2019-05-01',theme="white",name="GBP")
```



Moving averages comparison (SMA) for 20, 50 and 100 trading days.

Simple Moving Average (SMA)

```{r}
candleChart(AMZN, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addSMA(n=c(20, 50, 80))
candleChart(GOOG, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addSMA(n=c(20,50,80))
candleChart(BAC, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addSMA(n=c(20,50,80))

```



```{r}
getSymbols("AMZN", from="2019-01-01")
bA <- BBands(HLC=HLC(AMZN["2019"]), n=20, sd=2)
tail(bA,10)

getSymbols("GOOG", from="2019-01-01")
bG <- BBands(HLC=HLC(GOOG["2019"]), n=20, sd=2)
tail(bG,10)

getSymbols("BAC", from="2019-01-01")
bB <- BBands(HLC=HLC(BAC["2019"]), n=20, sd=2)
tail(bB,10)
```

Bollinger Bands Graph:

```{r}

chartSeries(AMZN, subset = "2019", theme="white")
addBBands(draw="p")
addVo()

chartSeries(GOOG, subset = "2019", theme="white")
addBBands(draw="p")
addVo()

chartSeries(BAC, subset = "2019", theme="white")
addBBands(draw="p")
addVo()


```

Moving Average Convergence-Divergence (MACD)

```{r}
macd <- MACD( Cl(AMZN), 12, 26, 9, maType="EMA" ) 
tail(macd)
chartSeries(AMZN, subset="2019",theme="white")
addMACD()

macd <- MACD( Cl(GOOG), 12, 26, 9, maType="EMA" ) 
tail(macd)
chartSeries(GOOG, subset="2019",theme="white")
addMACD()

macd <- MACD( Cl(BAC), 12, 26, 9, maType="EMA" ) 
tail(macd)
chartSeries(BAC, subset="2019",theme="white")
addMACD()
```

Relative Strength Index (RSI)

```{r}
rsi <- RSI( Cl(AMZN), n = 14 ) 
tail(rsi)
chartSeries(AMZN, subset="2019",theme="white")
addRSI()

rsi <- RSI( Cl(GOOG), n = 14 ) 
tail(rsi)
chartSeries(GOOG, subset="2019",theme="white")
addRSI()

rsi <- RSI( Cl(BAC), n = 14 ) 
tail(rsi)
chartSeries(BAC, subset="2019",theme="white")
addRSI()
```

Commodity Channel Index (CCI):
```{r}
candleChart(AMZN, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCCI()

candleChart(GOOG, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCCI()

candleChart(BAC, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCCI()
```

Directional Movement Indicator (DMI):
```{r}
candleChart(AMZN, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addADX()

candleChart(GOOG, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addADX()

candleChart(BAC, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addADX()
```

Chaiken Money Flow:

```{r}
candleChart(AMZN, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCMF()

candleChart(GOOG, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCMF()

candleChart(BAC, up.col = "black", dn.col = "red", theme = "white", subset = "2019-01/")
addCMF()
```

